---
title: "README"
format: gfm
---

# Meet the penguins

The three species of penguins we are looking at today are called Chinstrap, Gentoo and Adelie. They live on the islands of Biscoe, Dream and Torgersen. We have access to information about 344 different penguins, as shown below:

```{r}
#| echo: false
#| output: asis
library(palmerpenguins)
library(knitr)
library(dplyr)
kable(slice_sample(penguins, n = 10))

```

# What do we want to find out?

Here are some things we want to know about the penguins:

- Which island has the most penguins? Which island has the most Adelie penguins?
- Is there a relationship between bill length and bill depth? For example, do penguins with longer bills also have deeper bills?
- Do female penguins have longer or shorter flippers than male penguins?
- Which species of penguin has the longest flippers?
- How heavy is the heaviest penguin? Which species is the heaviest?
- Anything else you want to find out!

Work with your group to make a chart or a table answering your question.


```{r}
1 + 1
```

You can add options to executable code like this 

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
